A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2013-04-21 docs/paper_lncs.tex
Minor fix in paper

% the name(s) of the author(s) follow(s) next
\author{Russell Cohen\and Thomas Georgiou\and Pedram Razavi}
%
\authorrunning{A Reimplementation of Python’s dict}
% (feature abused for this document to repeat the title also on left hand pages)

@@

As mentioned before, another set of the benchmarks \cite{bench_suite} that we utilized was based on different standard real-world Python applications. We ran and timed the performance of the new implementation and CPython 2.7.3 side by side using the Python-Mirrors suite. The performance of more than ten applications were recoded as shown in the figures.

\begin{figure}
  \centering
  \includegraphics[width=12cm]{appsbench.pdf}
  \caption{Percentage of overall improvements in some real-world Python
  applications. Nearly none of the applications performed worse. Python Pickle
  and html5lib faster around 3\% to 4\%. }
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=12cm]{slowpickle.png}
  \caption{Python Pickle module benchmark. Minimum Iteration: changed from 0.705s to 0.681s: 1.04 times faster. Average iteration: changed from 0.710s to 0.686s: 1.04 times faster. Standard deviation of new implementation 2.0383 times smaller}
\end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=160mm]{lr-10.png}
%   \caption{}
% \end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=160mm]{lr-10.png}
%   \caption{}
% \end{figure}

In a couple of the programs such as pure Python Pickle (an object serialization
library) and html5lib (specification parser library) we calculated an
improvement of 3\% to 4\%. In other cases we did not calculate an speedup but
at the same time we did not find any real-world case which the new
implementation performs significantly slower. These results were consistent
with the previous results of PyBench that showed about 4.5\% improvement.

>>>>

% the name(s) of the author(s) follow(s) next
\author{Russell Cohen\and Thomas Georgiou\and Pedram Razavi}
%
\authorrunning{R. Cohen, T. Georgiou, P. Razavi}
% (feature abused for this document to repeat the title also on left hand pages)

@@

As mentioned before, another set of the benchmarks \cite{bench_suite} that we utilized was based on different standard real-world Python applications. We ran and timed the performance of the new implementation and CPython 2.7.3 side by side using the Python-Mirrors suite. The performance of more than ten applications is indicated in Fig.~\ref{fig:suite}.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=12cm]{appsbench.pdf}
  \caption{Percentage of overall improvements in some real-world Python
  applications. Nearly none of the applications performed worse. Python Pickle
  and html5lib faster around 3\% to 4\%. }
  \label{fig:suite}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=12cm]{slowpickle.png}
  \caption{Python Pickle module benchmark. Minimum Iteration: changed from 0.705s to 0.681s: 1.04 times faster. Average iteration: changed from 0.710s to 0.686s: 1.04 times faster. Standard deviation of new implementation 2.0383 times smaller}
  \label{fig:pickle}
\end{figure}

In a couple of the programs such as pure Python Pickle (an object serialization
library) and html5lib (specification parser library) we calculated an
improvement of 3\% to 4\% (Fig.~\ref{fig:pickle}). In other cases we did not calculate an speedup but
at the same time we did not find any real-world case which the new
implementation performs significantly slower. These results were consistent
with the previous results of PyBench that showed about 4.5\% improvement.
